Evolution of solar wind discontinuities in the inner heliosphere

### 2025-12-20 notes.qmd
docs: update figures and text
docs: publish as manuscript
docs: add AGU25 presentation

# Updates

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory
  - maybe just too localized anisotropy that is not well measured with available time resolution... 
  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy

@@

# TODO

- [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?

@@

![](figures/enc2/thickness_current)

![](figures/enc2/density_distribution)

![](figures/enc2/dvl)
:::

Pair plot

![](figures/enc2/dn-dT)

![](figures/enc2/dT-dB)

![](figures/enc2/dn-dB)
:::

>>>>

# TODO / Future work

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Why we have so many events from Wind observations?
  - Biased by different methods.
- [x] Show PSP and ARTEMIS examples with Bn/B~0.75?
  - [ ] Check $B_n$ dependence to check method bias (duration / thickness)
- [ ] Disagreement between anisotropy observed and predicted by the theory
  - maybe just too localized anisotropy that is not well measured with available time resolution... 
  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
- [ ] Check the occurrence rates correlation with fluctuation level / residual energy at similar radial distance.

@@

@@
